### 2020-06-01 paper.tex
Add Performance Metrics Subsection
Add Performance Comparisons Section

Insert performance metrics here

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SIMULATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Insert simulation output here

@@

Insert experiments comparisons here

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% OBSERVATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Observation}

Insert observation here

>>>>

The total wirelength and the time consumed finding the optimum solution are usually the chosen metrics whenever it comes to performance evaluation of placement algorithms. Due to the dependability of the time consumed by the machines on which algorithms are run, only the total wirelength is chosen.

@@

To assess the performance of the proposed algorithm implementation, three test cases are addressed and analyzed in the form of three experiments. In each experiment, the output total wirelength of the proposed algorithm implementation is compared to the output total wirelength of different standard algorithms used for solving the placement problem such as simulated annealing, a genetic algorithm.

\subsubsection{Experiment 1}

In this experiment, the input population size equals $4$.

\begin{table}[H]
    \caption{Experiment 1 Results}
    \centering
    \begin{tabular}{||c c c c c||}
        \hline
        \textit{\textbf{\# of Cells}} & \textit{\textbf{Initial Placement}} & \textit{\textbf{SA}} & \textit{\textbf{GA}} & \textit{\textbf{Proposed Algorithm}}\T \B \\
    \hline
    \hline
    7 & 66 & 48 & 45 & 44 \T \B\\ \hline
    20 & 245 & 170 & 156 & 151 \T \B\\ \hline
    40 & 375 & 348 & 335 & 296 \T \B\\ \hline
    52 & 461 & 461 & 426 & 394 \T \B\\ \hline
     \end{tabular}
    \label{table2}
\end{table}

\subsubsection{Experiment 2}

In this experiment, the input population size equals $8$.

\begin{table}[H]
    \caption{Experiment 2 Results}
    \centering
    \begin{tabular}{||c c c c c||}
        \hline
        \textit{\textbf{\# of Cells}} & \textit{\textbf{Initial Placement}} & \textit{\textbf{SA}} & \textit{\textbf{GA}} & \textit{\textbf{Proposed Algorithm}}\T \B \\
    \hline
    \hline
    7 & 52 & 40 & 36 & 30 \T \B\\ \hline
    20 & 209 & 169 & 159 & 131 \T \B\\ \hline
    40 & 452 & 351 & 288 & 281 \T \B\\ \hline
    52 & 557 & 467 & 391 & 388 \T \B\\ \hline
     \end{tabular}
    \label{table3}
\end{table}

\subsubsection{Experiment 3}

In this experiment, the input population size equals $20$.

\begin{table}[H]
    \caption{Experiment 3 Results}
    \centering
    \begin{tabular}{||c c c c c||}
        \hline
        \textit{\textbf{\# of Cells}} & \textit{\textbf{Initial Placement}} & \textit{\textbf{SA}} & \textit{\textbf{GA}} & \textit{\textbf{Proposed Algorithm}}\T \B \\
    \hline
    \hline
    7 & 62 & 45 & 29 & 29 \T \B\\ \hline
    20 & 240 & 170 & 127 & 125 \T \B\\ \hline
    40 & 383 & 343 & 223 & 219 \T \B\\ \hline
    52 & 510 & 453 & 313 & 316 \T \B\\ \hline
     \end{tabular}
    \label{table4}
\end{table}
